\name{}: machine learning over interaction networks and ontology-based background knowledge predicts drug--target interactions

### 2021-04-27 paper/main.tex
.

Considering Macro AUCs, \name{} improves significantly ($p<10^{-4}$,
one-sided t-test) over MolTrans ($t=36.6$), DeepDTI ($t=40.5$),
DeepDTA ($t=36.6$), and DeepConv-DTI ($t=40.5$) on the BioSnap
dataset, and significantly ($p<10^{-4}$, one-sided t-test) over DTINet
($t=20.8$) and DTIGEMS+ ($t=18.0$) on the Yamanishi dataset; DTI-CDF
performs significantly better than \name{} ($p=0.02$, one-sided
t-test).  We further perform another one-tailed t-test to compare
$MicroAUC_p$ performance. We find that \name{} improved significantly
($p < 10^{-4}$) over MolTrans($t=21.2$), DeepDTI ($t=31.0$), DeepDTA
($t=33.4$), and DeepConv-DTI ($t=23.7$) on the BioSnap dataset, and
over DTINet ($t=29.6$), DTIGEMS+ ($t=28.0$), and DTI-CDF ($t=9.5$) on
the Yamanishi dataset.

>>>>

Considering Macro AUCs, \name{} improves significantly ($p<10^{-4}$,
one-sided t-test) over MolTrans ($t=36.6$), DeepDTI ($t=40.5$),
DeepDTA ($t=36.6$), and DeepConv-DTI ($t=40.5$) on the BioSnap
dataset, and significantly ($p<10^{-4}$, one-sided t-test) over DTINet
($t=20.8$) and DTIGEMS+ ($t=18.0$) on the Yamanishi dataset; DTI-CDF
performs better than \name{} ($p=0.02$, one-sided t-test).  We further
perform another one-tailed t-test to compare $MicroAUC_p$
performance. We find that \name{} improved significantly
($p < 10^{-4}$) over MolTrans($t=21.2$), DeepDTI ($t=31.0$), DeepDTA
($t=33.4$), and DeepConv-DTI ($t=23.7$) on the BioSnap dataset, and
over DTINet ($t=29.6$), DTIGEMS+ ($t=28.0$), and DTI-CDF ($t=9.5$) on
the Yamanishi dataset.
